\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}

\section{A.2.3(a)(c)}

\subsection{Part (a)}

Describe the sets

\begin{equation}
	\bigcup_{n=1}^{\infty}(-1/n,1/n)
\end{equation}

and

\begin{equation}
	\bigcap_{n=1}^{\infty}(-1/n,1/n)
\end{equation}

I'll start off with some concrete examples of the first set.
This is a series of open intervals of decreasing size.

\begin{equation}
	(-1,1) \cup (-\frac{1}{2},\frac{1}{2})\cup (-\frac{1}{3},\frac{1}{3})\cup (-\frac{1}{4},\frac{1}{4}) ...
\end{equation}

I see this as a bunch of nested boxes.
As $n$ increases, the interval (AKA the box) gets smaller.
Since this is a union and the bounds of the smaller box are narrower than the larger box, we can keep stuffing boxes into one another.
A bit of nuance here is that the endpoints of the smaller interval exist in the larger inverval.
The way I think of this is that we discard the wrapping paper of the smaller box when combining items.
I do not believe this results in any gaps (or holes) in the union, but feel free to correct my logic!
Due to the fact that we are working with sets, once we remove duplicates, we are left with the first and largest open inverval $(-1,1)$.

\paragraph{}

Here is an example of the second set.

\begin{equation}
	(-1,1) \cap (-\frac{1}{2},\frac{1}{2})\cap (-\frac{1}{3},\frac{1}{3})\cap (-\frac{1}{4},\frac{1}{4}) ...
\end{equation}

This results in the same progression of smaller intervals, but we are now dealing with the intersection of intervals.
We only account for items in both boxes and discard the excess.
As $n$ grows, the interval shrinks and so does the amount of common material between one box and the next.

\begin{equation}
	(-1,1) \cap (-\frac{1}{2},\frac{1}{2}) = (-\frac{1}{2},\frac{1}{2})
\end{equation}

\begin{equation}
	(-\frac{1}{2},\frac{1}{2}) \cap (-\frac{1}{3},\frac{1}{3}) = (-\frac{1}{3},\frac{1}{3})
\end{equation}

\begin{equation}
	(-\frac{1}{3},\frac{1}{3}) \cap (-\frac{1}{4},\frac{1}{4}) = (-\frac{1}{4},\frac{1}{4})
\end{equation}

The end result is an infinitely small {\bf open} interval centered around $0$.

\subsection{Part (c)}

Describe the sets

\begin{equation}
	\bigcup_{n=1}^{\infty}[n,n+1]
\end{equation}

and

\begin{equation}
	\bigcap_{n=1}^{\infty}[n,n+1]
\end{equation}

Starting with the first set, it begins with the following sequence.

\begin{equation}
	[1,2]\cup[2,3]\cup[3,4]\cup[4,5]...
\end{equation}

Since these are all closed intervals, the endpoints are included in the sets.
The union results in a range that is closed from $1$ to $n$.

\begin{equation}
	[1,2], [1,3], [1,4], [1,5]...[1,n]
\end{equation}

Since $n$ goes to infinity, this is the same as the semiopen interval $[1,\infty)$.

In the second set, we replace union with intersection.

\begin{equation}
	[1,2]\cap[2,3]\cap[3,4]\cap[4,5]...
\end{equation}

The only common items in any two consecutive sets are the endpoints between them.
This results in a sequence of natural numbers starting with 2 (since 1 is not in tne first intersection).

\begin{equation}
	\{2,3,4,5...n\}
\end{equation}

The end result is the infinite sequence $\{x: x > 1, x \in \mathbb{N}\}$.

\end{document}
